Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-13 trunk/constantRate/ConstCompFuzzExt.tex
Working on proof

\begin{itemize}
\item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is still large~(\clref{cl:many locations ent}).
\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view.
\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy).  
\end{itemize}

\begin{lemma}
\label{lem:blocks unguessable after queries}
Let $n$ be a security parameter.  Let $W(n) = W = W_1,..., W_\ell$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.  Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.  %Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}. 
Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.  Furthermore, since $W_i$ are independent $\Hav(W | View(A))= \omega(\ell \log n)$.
\end{lemma}
\begin{proof}
Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  (There is dependency between $W_i$ and the queries but it is all contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$.  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&= \omega(\log n) - \log |A'|\\
&= \omega(\log n) - \log (q+1) = \omega(\log n) - O(\log(n)) = \omega(\log n)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
%There are two possible outcomes to an equality query $1$ in which case $\Hoo(W|Q = q_w) = 0$ and $0$ in which case $\Hoo(W| Q =q_w ) \geq -\log 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})$~(every remaining outcome is scaled by the $w$ not being a possible outcome).  Thus,
%\begin{align*}
%\Hav(W | Q_w) &= -\log \left(\Pr[W=w]2^{-0} + \Pr[W\neq w] 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})\right)\\
%&\geq -\log \left(2^{-k} + (1-2^{-k})2^{-k}(1-2^{-k})\right)\\
%&\geq -\log \left(2^{-(k)}(1+(1-2^{-k})^2)\right)\geq k-1
%\end{align*}
%Now consider the distribution $W' = W | W\neq w$, by the same argument asking a single query of $W'$ reduces it min-entropy by at most one bit~(we need only consider the case where previous responses were all zeros as the entropy is already $0$ if a previous response is $1$).  Thus, for some polynomial number of queries $n_q$ we have that $\Hav(W | Q_1,..., Q_{n_q}) = k - n_q$.  Thus for $k = \omega(\log n)$ and $n_q = \poly(n)$\bnote{this is too big a loss} %we have that $k-n_q = \omega(\log n)$.  This completes the proof of the lemma. 
\end{proof}
Let $\mathcal{I}$ be the set of all indices $\{1,..., n\}$.  Then $\Hav(C | C_{\mathcal{I}^c}) = \Hoo(C) = \ell$.  We know show that all codewords different in only positions of $\mathcal{I}$ are indistinguishable.
\begin{lemma}
Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then let $D$ be an unbounded distinguisher 
\[
\Pr[D( View(A), C_{\mathcal{I}^c}) =1 | C = c_1] - \Pr[D(View(A), C_{\mathcal{I}^c}) = 1 | C= c_2] < \ngl(n).
\]
\end{lemma}

\begin{lemma}
\bnote{what goes here?}
Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
\end{lemma}
\begin{lemma}
\label{lem:super log indist by equal queries}
Let $W$ and $U$ be two distributions of super-logarithmic entropy.  Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
\end{lemma}
\begin{proof}
It suffices to show that with the probability of all responses being $0$ is overwhelming.  Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.  \bnote{Finish this proof}
\end{proof}

\begin{lemma}
\label{lem:code bits statistically indist}
Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.  Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
\end{lemma}
\begin{proof}
\bnote{Do this}
\end{proof}
We can extend this lemma to the entire codeword $C$:
\begin{lemma}
For all $c_1, c_2 \in C$ we have the following: 
\[
\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
\]
\end{lemma}
\begin{lemma}
If $C$ is output then, for all $i$, $\Hav(C_i |View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)}))\geq 1 - \ngl(n)$.
\end{lemma}
\begin{proof}
Since $C$ is output equiprobable we know that for each $i$, $\Pr[C_i =1 ] = 1/2$.  Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).  For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$. 
\begin{align*}
\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C_i =b | view ] &\leq 1/2 + \ngl(n)\\
\end{align*}
If this was not true~(that is in expectation, there was some $b$ that was likely with probability greater than $1/2+1/\poly(n)$), there there would exist an unbounded adversary outputting that $b$, contradicting \lemref{lem:code bits statistically indist}).  
Taking the negative log of each side one has:
\begin{align*}
\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
 &=\\-\log \left(\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\max_{b\in\{0,1\}}\Pr[C_i =b | view ]  \right) &\geq -\log (1/2 + \ngl(n))\\
&\geq -\log(\frac{1}{2} + \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+2}{2n^{w}}\right)\\
%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
&=1-\left(\log (1+\frac{2}{n^e}) \right)\\
&=1-\frac{1}{\ln 2}\left(\ln (1+\frac{2}{n^e}) \right)\\
&= 1- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{2}{n^e})^i\right) \\
&\geq 1 - \frac{1}{\ln 2} \frac{2}{n^e} = 1-\ngl(n)
\end{align*}
Here the second to last line is derived using the Taylor expansion for $\ln(1+x)$ and the last line is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive.
\end{proof}
By similar reasoning we can extend this lemma to the entire codeword:
\begin{lemma}
If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
\end{lemma}
%\begin{lemma}
%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
%\end{lemma}

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that 
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}
As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}.

>>>>

\begin{itemize}
\item Show that conditioned on the adversary's view there is a large set of blocks, $\mathcal{I}$, that have a super logarithmic entropy~(\lemref{lem:blocks unguessable after queries}).
\item Show that conditioned on the values of all other indices, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view~(\lemref{lem:codewords in I close}).
%\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
\item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
\end{itemize}

\begin{lemma}
\label{lem:blocks unguessable after queries}
Let $n$ be a security parameter.  Let $W(n) = W = W_1,..., W_\ell$ be a distribution where each $W_i$ is independent of all $W_j$ and $\forall i, \Hoo(W_i) = \omega(\log n)$.  Then let $\mathcal{A}$ be an adversary making a polynomial number of oracle equality queries for blocks $i$.  %Let $C = c_1,.., c_\ell$ be as in \consref{cons:informal construction}. 
Then $\forall i, \Hav(W_i | View(A))  = \omega(\log n)$.  Furthermore, since $W_i$ are independent $\Hav(W | View(A))= \omega(\ell \log n)$.
\end{lemma}
\begin{proof}
Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  (There is dependency between $W_i$ and the queries but it is all contained in $A_{w_1},..., A_{w_q}$.)  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$.  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&= \omega(\log n) - \log |A'|\\
&= \omega(\log n) - \log (q+1) = \omega(\log n) - O(\log(n)) = \omega(\log n)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
%There are two possible outcomes to an equality query $1$ in which case $\Hoo(W|Q = q_w) = 0$ and $0$ in which case $\Hoo(W| Q =q_w ) \geq -\log 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})$~(every remaining outcome is scaled by the $w$ not being a possible outcome).  Thus,
%\begin{align*}
%\Hav(W | Q_w) &= -\log \left(\Pr[W=w]2^{-0} + \Pr[W\neq w] 2^{-\Hoo(W)}(1 - 2^{-\Hoo(W)})\right)\\
%&\geq -\log \left(2^{-k} + (1-2^{-k})2^{-k}(1-2^{-k})\right)\\
%&\geq -\log \left(2^{-(k)}(1+(1-2^{-k})^2)\right)\geq k-1
%\end{align*}
%Now consider the distribution $W' = W | W\neq w$, by the same argument asking a single query of $W'$ reduces it min-entropy by at most one bit~(we need only consider the case where previous responses were all zeros as the entropy is already $0$ if a previous response is $1$).  Thus, for some polynomial number of queries $n_q$ we have that $\Hav(W | Q_1,..., Q_{n_q}) = k - n_q$.  Thus for $k = \omega(\log n)$ and $n_q = \poly(n)$\bnote{this is too big a loss} %we have that $k-n_q = \omega(\log n)$.  This completes the proof of the lemma. 
\end{proof}
Let $\mathcal{I}$ be the set of all indices $\{1,..., n\}$.  Then $\Hav(C | C_{\mathcal{I}^c}) = \Hoo(C) = \ell$.  We know show that all codewords different in only positions of $\mathcal{I}$ are indistinguishable.
\begin{lemma}
\label{lem:codewords in I close}
Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
\[
\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < \ngl(n).
\]
\end{lemma}
\begin{proof}
Recall by assumption that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \omega(\log n)$.  The only information about $C_i$ is contained in the query responses.  Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with overwhelming probability all responses to $c_i$ are $0$.  Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $1/\poly(n)$.  Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is negligible~(occurs with probability at most $q/2^n$).  Thus, it must occur with $1/\poly(n)$ probability when $c_i=0$.  When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with $1/\poly(n)$ probability this violates the super-logarithmic conditional min-entropy condition.  Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ all distinguishers are negligibly close.
\end{proof}

%\begin{lemma}
%\bnote{what goes here?}
%Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
%\end{lemma}
%\begin{lemma}
%\label{lem:super log indist by equal queries}
%Let $W$ and $U$ be two distributions of super-logarithmic entropy.  Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
%\end{lemma}
%\begin{proof}
%It suffices to show that with the probability of all responses being $0$ is overwhelming.  Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.  \bnote{Finish this proof}
%\end{proof}

%\begin{lemma}
%\label{lem:code bits statistically indist}
%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.  Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
%\end{lemma}
%\begin{proof}
%\bnote{Do this}
%\end{proof}
%We can extend this lemma to the entire codeword $C$:
%\begin{lemma}
%For all $c_1, c_2 \in C$ we have the following: 
%\[
%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
%\]
%\end{lemma}
The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
\begin{lemma}
Let $c\in C|C_{\mathcal{I}^c}$, then $\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n)$
\end{lemma}
\begin{proof}
Let $c\in C|C_{\mathcal{I}^c}$.  Let $P_c =\Pr[C=c | C_{\mathcal{I}^c}]$.  
%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).  For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$. 
\begin{align*}
\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c | C_{\mathcal{I}^c} \wedge view ] &\leq \Pr[C=c | C_{\mathcal{I}^c} ]+ \ngl(n) = P_c+\ngl(n)\\
\end{align*}
If this was not true~(that is in expectation, the probability of $c$ increased by a polynomial factor, then the statistical distance between $c$ and some other codeword $c'$ would be $1/\poly(n)$ violating \lemref{lem:codewords in I close}.
\end{proof}
\begin{corollary}
\label{cor:avg min after view}
$\Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
\end{corollary}
\begin{proof}
Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
Taking the negative log of the above lemma one has:
\begin{align}
\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
 &=\\-\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\\
&\geq -\log(P_c+ \frac{1}{n^{w}} )= -\log \left(\frac{n^{w}+P_c}{P_c n^{w}}\right)\\
%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\\
&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \\
&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
&= |C| - |\mathcal{I}^c| -\ngl(n)\label{eq:min ent}
\end{align}
Here the Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
\end{proof}

%\begin{lemma}
%\label{lem:obf has hill ent}
%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
%\end{lemma}
%\begin{proof}
%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.  Let $ (X, Y)  = (C, 
%\end{proof}
%By similar reasoning we can extend this lemma to the entire codeword:
%\begin{lemma}
%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
%\end{lemma}
%\begin{lemma}
%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
%\end{lemma}

@@

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that 
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}
As long as $\beta$ is small enough, we can show security of \consref{cons:first construction}~(replace \lemref{lem:blocks unguessable after queries} with an unguessable source, the rest of the arguments follow the same way).
